Using Genetic Algorithms to Find Approximations for the Minimum Vertex Cover Problem

### 2018-02-26 paper.tex
some weird error in texmaker

% preferences
\graphicspath{ {images/} }
\newcommand{\lineSeparationLength}{2mm}
\hypersetup{colorlinks=true, allcolors=black}
\addbibresource{references.bib}
\ExecuteBibliographyOptions{
	giveninits=false,
	isbn=false,
	doi=false,
	url=false
}
\setlength{\parskip}{1em}
\newcommand{\textem}[1]{\textbf{\emph{#1}}}
\newtheorem{lemma}{Lemma}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\algnewcommand\algorithmicto{\textbf{to}}
\algrenewtext{For}[3]%
{\algorithmicfor\ #1 = #2 \algorithmicto\ #3 \algorithmicdo}

@@

\vspace{-10mm}
\begin{center}
Keywords: genetic algorithms, NP-complete, combinatorial optimization, non-deterministic algorithms, approximation algorithms, minimum vertex cover.
\end{center}

@@

They considered regular graphs\footnote{%
by regular graphs we don't refer to the definition where
each vertex has the same degree.
}, each of which consists of three levels.
The first two levels have the same
number of nodes while the third level has two nodes less
than the number of nodes found on the previous two
levels.
More precisely, each graph consists of $n = 3k + 4 \ (k \geq 1)$
nodes; $k+2$ nodes on the first level, labeled $1, 2, \dots, k+2$;
followed by $k+2$ nodes on the second level, labeled $k+3, \dots, 2k+4$;
while the $k$ nodes of the third level are labeled $2k+5, \dots, 3k+4$.
The regular graph for $k = 3$ can be found in figure~\ref{fig:ps}.
A minimum vertex cover is obtained by choosing all
the nodes of the second level, but the greedy strategy
would start with the nodes of the third level, since these
have highest degree. Consequently, the greedy strategy
finds a solution of size $2k + 2$ (since it has to select $k + 2$
nodes in addition to the nodes of the third level), while
the optimal solution has size $k + 2$.

@@

\begin{table}[!htbp]
\centering
\includegraphics[width=1\textwidth]{t1}
\caption{general schema for genetic algorithms}
\label{tbl:t1}
\end{table}

@@

\begin{table}[!htbp]
\centering
\includegraphics[width=1\textwidth]{t2}
\caption{general schema for genetic algorithms}
\label{tbl:t2}
\end{table}

@@

\begin{table}[!htbp]
\centering
\includegraphics[width=1\textwidth]{t3}
\caption{general schema for genetic algorithms}
\label{tbl:t3}
\end{table}

\begin{table}[!htbp]
\centering
\includegraphics[width=1\textwidth]{t4}
\caption{general schema for genetic algorithms}
\label{tbl:t4}
\end{table}

% herereh
\subsection{Experimental Conclusions}
From these tables, a number of interesting conclusions
can be drawn. For the random graphs used to compare the
genetic algorithm and the vercov algorithm,
it is known by construction that an optimum of quality 55 exists in the first test set,
(respectively, an optimum of quality 110 exists for the second test set). This optimum is likely to be the
global optimum, And it is found by the genetic
algorithm at least once within the $N = 100$ runs that were performed.

@@

In case of the regular graph after Papadimitriou and
Steiglitz, the genetic algorithm is able to find the global
optimum in about $2/3$ of all runs, while the remaining
runs identify a solution of quality $2k + 2$.
Whereas, vercov algorithm gives a solution of quality $2k + 2$ in all of the 100 runs as expected.
Recall that the graphs are constructed
so as to force the vercov algorithm into yielding solutions
of quality $2k + 2$.
The random choice of edges in line~\ref{alg:rand} of the algorithm implies that nodes from either layers one and two, or layers two and three are involved in the solution being constructed, which in turn implies that two layers have to be part of the solution found by the algorithm [10]mvcp.

For the randomly constructed graphs, the vercov algorithm performs
poorly.
It barely finds solutions of quality 80 (for graphs of size 100) and 172 (for graphs of size 200).
The average performance of the vercov algorithm (surprisingly)
decreases as the edge density is increased.
i.e. the problems become even harder for the vercov algorithm
while they become much simpler for the genetic algorithm when
the edge density increases.
The average fitness found by the genetic algorithm is notably
better than the one found by the vercov algorithm.
One can demonstrate this by calculating
the ratio of the absolute (or equivalently the relative) error.
For example, for the first problem instance,
let $\bar{f}_1, \bar{f}_2$ be the average found by
the genetic algorithm, vercov algorithm respectively.
We have $ (\bar{f}_2 - 55) / (\bar{f}_1 - 55) = (86.46 - 55)/(62.61 - 55) \approx 4 = 400\%$
that is, the error was reduced by a factor of 4.

\section{Conclusion}
In this work, we have demonstrated that genetic algorithms can be used in a straightforward way t
good approximate solutions of the minimum vertex cover
problem. Moreover, the results found by the genetic algorithm are better than those obtained from the best
known traditional heuristic, the vercov algorithm. These, in addition to other good results obtained on, highly constrained combinatorial optimization
problems such as the subset sum [7], minimum tardy
task [7], and multiple knapsack problems [8], give strong
evidence that genetic algorithms can yield good solutions for a wide range of hard combinatorial optimization problems for which solutions can be represented by
binary strings. \cite[p.~400, p.]{mvcp-back, goldberg} \cite{coley}

>>>>

% preferences
\graphicspath{ {images/} }
\newcommand{\lineSeparationLength}{2mm}
\hypersetup{colorlinks=true, allcolors=black}
\addbibresource{references.bib}
\ExecuteBibliographyOptions{
	giveninits=false,
	isbn=false,
	doi=false,
	url=false
}
\setlength{\parskip}{1em}
\newcommand{\textem}[1]{\textbf{\emph{#1}}}
\newtheorem{lemma}{Lemma}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\algnewcommand\algorithmicto{\textbf{to}}
\algrenewtext{For}[3]%
{\algorithmicfor\ #1 = #2 \algorithmicto\ #3 \algorithmicdo}
\captionsetup{font=footnotesize}

@@

\vspace{-10mm}
\begin{center}
Keywords: minimum vertex cover, NP-complete, genetic algorithms,\\
combinatorial optimization, approximation algorithms.
\end{center}

@@

They considered regular graphs\footnote{%
by ``regular graphs'' we don't refer to the definition where
each vertex has the same degree.
}, each of which consists of three levels.
The first two levels have the same
number of nodes while the third level has two nodes less
than the number of nodes found on the previous two
levels.
More precisely, each graph consists of $n = 3k + 4 \ (k \geq 1)$
nodes; $k+2$ nodes on the first level, labeled $1, 2, \dots, k+2$;
followed by $k+2$ nodes on the second level, labeled $k+3, \dots, 2k+4$;
while the $k$ nodes of the third level are labeled $2k+5, \dots, 3k+4$.
The regular graph for $k = 3$ can be found in figure~\ref{fig:ps}.
A minimum vertex cover is obtained by choosing all
the nodes of the second level, but the greedy strategy
would start with the nodes of the third level, since these
have highest degree. Consequently, the greedy strategy
finds a solution of size $2k + 2$ (since it has to select $k + 2$
nodes in addition to the nodes of the third level), while
the optimal solution has size $k + 2$.

@@

\begin{table}[!htbp]
\centering
\includegraphics[width=1\textwidth]{t1}
\caption{%
Experimental results obtained by the genetic algorithm for five random graphs of size $n = 100$ with edge density: $d = 0.1$ (``mvcp100-01''), $d = 0.2$ (``mvcp100-02''), $d = 0.3$ (``mvcp100-03''), $d = 0.5$ (``mvcp100-04''), $d = 0.5$ (``mvcp100-05'') and the regular graph of size $n = 100 \ (k=32)$ from Papadimitriou and Steiglitz (``PS100'').%
}
\label{tbl:t1}
\end{table}

@@

\begin{table}[!htbp]
\centering
\includegraphics[width=1\textwidth]{t2}
\caption{%
Experimental results obtained by the vercov algorithm for five random graphs of size $n = 100$ with edge density: $d = 0.1$ (``mvcp100-01''), $d = 0.2$ (``mvcp100-02''), $d = 0.3$ (``mvcp100-03''), $d = 0.5$ (``mvcp100-04''), $d = 0.5$ (``mvcp100-05'') and the regular graph of size $n = 100 \ (k=32)$ from Papadimitriou and Steiglitz (``PS100'').%
}
\label{tbl:t2}
\end{table}

@@

\begin{table}[!htbp]
\centering
\includegraphics[width=1\textwidth]{t3}
\caption{%
Experimental results obtained by the genetic algorithm for five random graphs of size $n = 200$ with edge density: $d = 0.1$ (``mvcp200-01''), $d = 0.2$ (``mvcp200-02''), $d = 0.3$ (``mvcp200-03''), $d = 0.5$ (``mvcp200-04''), $d = 0.5$ (``mvcp200-05'') and the regular graph of size $n = 202 \ (k=66)$ from Papadimitriou and Steiglitz (``PS202'').%
}
\label{tbl:t3}
\end{table}

\begin{table}[!htbp]
\centering
\includegraphics[width=1\textwidth]{t4}
\caption{%
Experimental results obtained by the vercov algorithm for five random graphs of size $n = 200$ with edge density: $d = 0.1$ (``mvcp200-01''), $d = 0.2$ (``mvcp200-02''), $d = 0.3$ (``mvcp200-03''), $d = 0.5$ (``mvcp200-04''), $d = 0.5$ (``mvcp200-05'') and the regular graph of size $n = 202 \ (k=66)$ from Papadimitriou and Steiglitz (``PS202'').%
}
\label{tbl:t4}
\end{table}

\subsection{Experimental Conclusions}
From these tables, a number of interesting conclusions
can be drawn.
For the random graphs used to compare the
genetic algorithm and the vercov algorithm,
it is known by construction that an optimum of
quality 55 exists for test set 1,
(respectively, an optimum of quality 110 exists
for the test set 2).
This optimum is likely to be the global optimum.
And it is found by the genetic algorithm at least once
within the $N = 100$ runs that were performed.

@@

In case of the regular graph after Papadimitriou and
Steiglitz, the genetic algorithm is able to find the global
optimum in about $2/3$ of all runs, while the remaining
runs identify a solution of quality $2k + 2$.
Whereas, vercov algorithm gives a solution of
quality $2k + 2$ in all of the 100 runs as expected tocite{[10] mvcp}.
Recall that the graphs are constructed
so as to force the vercov algorithm into yielding solutions
of quality $2k + 2$.
The random choice of edges (line~\ref{alg:rand} of algorithm~\ref{alg:vercov})
implies that nodes from either layers one and two, or layers two and three
are involved in the solution being constructed,
which in turn implies that two layers have to be part of the solution
found by the algorithm.

For the randomly constructed graphs, the vercov algorithm
performs poorly.
It barely finds solutions of quality 80 (for graphs of size 100)
and 172 (for graphs of size 200).
The average performance of the vercov algorithm (surprisingly)
decreases as the edge density is increased;
i.e. the problems become even harder for the vercov algorithm
while they become much simpler for the genetic algorithm when
the edge density increases.
The average fitness found by the genetic algorithm is notably
better than the one found by the vercov algorithm.
One can demonstrate this by calculating
the ratio of the absolute (or equivalently, the relative) error.
For example, for the first problem instance,
let $\bar{f}_1, \bar{f}_2$ be the average found by
the genetic algorithm, vercov algorithm respectively.
We have $ (\bar{f}_2 - 55) / (\bar{f}_1 - 55) = (86.46 - 55)/(62.61 - 55) \approx 4 = 400\%$
that is, the error was reduced by a factor of 4.

\section{Conclusion}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod
tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam,
quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo
consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse
cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non
proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
